Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-08-07 table_of_variables_and_constants.tex
Correcting another error associated with the Jeans refinement criterion.  The equation doesn't include a factor of mu or gamma which are in the code.

  \multicolumn{2}{l}{\underline{Star Formation And Feedback}} \\[5pt]
  $t_{\rm cool}$ & cooling time \\
  $t_{\rm dyn}$ & local dynamical time \\
  $t_{\rm form}$ & star particle formation time \\
  $m_{\rm b}$ & baryonic mass of cell \\
  $m_{\rm J}$ & Jeans mass of cell \\
  $m_*$ & star particle mass \\
  $m_{\rm *min}$ & minimum star particle mass \\
  $f_{\rm *eff}$ & star formation efficiency parameter \\
  $f_{\rm Zb}$ & metallicity fraction of baryon gas in cell \\
  $f_{\rm m*}$ & fraction of star particle's mass returned to cell \\
  $f_{\rm Z*}$ & fraction of star particle's metal mass returned to cell \\
  $f_{\rm SN}$ & fraction of stellar rest mass energy deposited as feedback \\
  $\Delta m_{\rm sf}$ & mass of stars formed in current timestep \\
  $E_{\rm add}$ & feedback energy added to cell \\
  $T_{\rm dyn,min}$ & user-defined minimum dynamical time \\
  $\eta$ & overdensity threshold for star formation \\
  $\rho_{\rm SF}$ & constant proper density threshold for star formation \\
  $\tau_*$ & characteristic star formation timescale (for Schmidt-Law method) \\[3pt]

>>>>

  \multicolumn{2}{l}{\underline{Star Formation And Feedback}} \\[5pt]
  $t_{\rm cool}$ & cooling time \\
  $t_{\rm dyn}$ & local dynamical time \\
  $t_{\rm form}$ & star particle formation time \\
  $m_{\rm b}$ & baryonic mass of cell \\
  $m_{\rm J}$ & Jeans mass of cell \\
  $m_*$ & star particle mass \\
  $m_{\rm *min}$ & minimum star particle mass \\
  $f_{\rm *eff}$ & star formation efficiency parameter \\
  $f_{\rm Zb}$ & metallicity fraction of baryon gas in cell \\
  $f_{\rm m*}$ & fraction of star particle's mass returned to cell \\
  $f_{\rm Z*}$ & fraction of star particle's metal mass returned to cell \\
  $f_{\rm SN}$ & fraction of stellar rest mass energy deposited as feedback \\
  $\Delta m_{\rm sf}$ & mass of stars formed in current timestep \\
  $E_{\rm add}$ & feedback energy added to cell \\
  $T_{\rm dyn,min}$ & user-defined minimum dynamical time \\
  $\eta$ & overdensity threshold for star formation \\
  $\rho_{\rm SF}$ & constant proper density threshold for star formation \\
  $\tau_*$ & characteristic star formation timescale (for Schmidt-Law method) \\[3pt]
  $\mu$ & mean molecular weight
